Supporting information: Copulas reveal complex and informative dependencies propagating throughout ecology

### 2019-05-14 Paper.Rmd

---
title: "Complex and informative dependencies propagate throughout ecology and can be revealed using copulas"
author: "Shyamolina Ghosh, Lawrence W. Sheppard, Mark T. Holder, Terrance E. Loecke, Philip C. Reid, James D. Bever, Daniel C. Reuman"
date: ""
geometry: "left=1.5cm,right=1.5cm,top=2.5cm,bottom=2.8cm"

@@

\noindent \emph{Possible alternative titles:}

@@

The importance of copulas in ecology

>>>>

---
title: "Copulas reveal complex and informative dependencies propagating throughout ecology"
author: "Shyamolina Ghosh, Lawrence W. Sheppard, Mark T. Holder, Terrance E. Loecke, Philip C. Reid, James D. Bever, Daniel C. Reuman"
date: ""
geometry: "left=1.5cm,right=1.5cm,top=2.5cm,bottom=2.8cm"

@@

<!--\noindent \emph{Possible alternative titles:}

Complex and informative dependencies propagate throughout ecology and can be revealed using copulas

@@

The importance of copulas in ecology-->

### 2019-05-14 SupportingInformation.Rmd

---
title: "Supporting Information : Complex and informative dependencies propogate throughout ecology and can be revealed using copulas"
author: "Shyamolina Ghosh, Lawrence W. Sheppard, Mark T. Holder, Terrance E. Loecke, Philip C. Reid, James D. Bever, Daniel C. Reuman"
geometry: "left=1cm,right=1cm,top=2.2cm,bottom=2.2cm"

>>>>

---
title: "Supporting information: Copulas reveal complex and informative dependencies propagating throughout ecology"
author: "Shyamolina Ghosh, Lawrence W. Sheppard, Mark T. Holder, Terrance E. Loecke, Philip C. Reid, James D. Bever, Daniel C. Reuman"
geometry: "left=1cm,right=1cm,top=2.2cm,bottom=2.2cm"
